\chapter Preliminary and Expected Results

Preliminary results are: 1 workshop paper at AAMAS, 1 invited talk at Bessensap. 
Current status of progress: ontology: status, agents: first OWL agent, display logic: basic show/no show properties per role and geographical position of the actor. 
In the near future, another journal paper on completing the agent design and implementation is awaiting submission. A conference paper on the ontology and the display logic is planned after conducting an end-user experiment on how to achieve situational awareness with furnishing or not different types of information to different users. The current ontology will be replaced shortly after all the modules and the comprehensive ontology design is worked out to the detail. A full validation and evaluation is following the pipeline for ensuring the level of adequacy of the ontology to the project.
In the distant future, more reasoning power is requested from the agents, that now should be able to have a very high control over the visual interface of the user. 

\chapter Publication Plan

The publication plan consists of one to two high-ranked conference papers or one journal paper. 

\chapter Doctoral Education Plan

The doctoral education plan foresees a total of 45 credit points in the course of the total 4 years of the doctorate program. There are several ways to achieve credits, and these are categorized into three: research-related, transferrable skills and disciplinary blabla. So far, x credits have been achieved in the category of transferrable skills through attending classes organized by the Graduate School, and x credits have been achieved from attending classes on the topic, and 1 credit for an accepted workshop paper at the AAMAS 2015 conference on Autonomous Agents and Mulit-Agent Systems.
In the future, more research skills are planned.
Teaching a lecture tutorial.
Other papers as described in the previous chapters.